---
title: "Data Exploration"
output: pdf_document
---

# Introduction

This notebook presents an exploratory data analysis (EDA) of the air quality dataset. The analysis involves loading the data, summarizing it, and generating visualizations to understand its structure and characteristics.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../src/data_exploration.R")
```


# Load Data

Load the Dataset Using the load_data Function

```{r load_data}
file_path <- '../data/raw/AirQualityUCI.xlsx'
data <- load_data(file_path)
head(data)
```


# Summarize Data

Summarize the Data to Get an Overview of Its Structure and Statistics

```{r summarize}
summarize_data(data)
```


# Missing Values

Check for Missing Values in the Dataset

```{r}
missing_values <- count_missing_values(data)
print(missing_values)
```


# Impute Missing Values

Impute the Missing Values Using Linear Interpolation

```{r}
data <- impute_missing_values(data)
```


# Summarize Data After Imputation

Summarize the Data Again After Imputing the Missing Values to See the Changes

```{r}
summarize_data(data)
```


# Time Series Plots

Plot the Time Series Data to Visualize the Trends and Patterns of Different Gas Concentrations and Environmental Factors

```{r}
plot_time_series(data, 'C6H6(GT)', 'C6H6(GT) Time Series Data')
plot_time_series(data, 'PT08.S2(NMHC)', 'PT08.S2(NMHC) Time Series Data')
plot_time_series(data[(1:24*30*12),], 'C6H6(GT)', 'C6H6(GT) Time Series Data')
```


# Correlation Analysis

Perform Correlation Analysis to Understand the Relationships Between Different Variables in the Dataset

```{r}
correlation_columns <- c('C6H6(GT)', 'PT08.S2(NMHC)', 'T', 'RH')
plot_correlations(data, correlation_columns)
```


# Distribution Analysis

Visualize the Distribution of Each Variable to Understand Their Spread and Identify Any Potential Skewness or Abnormalities

```{r}
data_distribution(data, 'C6H6(GT)', 'C6H6(GT) Data Distribution')
```


# Aggregate to Daily Data (Downsampling)

Aggregate the Data to a Daily Level

```{r}
data_daily <- aggregate_to_daily(data)
head(data_daily)
```


# Time Series Plots

Plot the Time Series Data to Visualize the Trends and Patterns of Benzene Concentration and Other Environmental Factors

```{r}
plot_time_series(data_daily, "daily_avg_benzene", "Daily Average Benzene Concentration")
```

# Decomposition

```{r}
plot_decomposition(data_daily, "daily_avg_benzene", freq = 7)
```

Decomposition Conclusions:
* No Trend
* Weekly Seasonality
* Data Has a Random Noise

# Decomposition - ALT Plot

```{r}
plot_decomposition_ggplot(data_daily, "daily_avg_benzene", freq = 7)
```
