---
title: "Experimental Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../src/experimental_analysis.R")
load("../data/processed/data_daily")
```


# Time Series Plots

Plot the Time Series Data to Visualize the Trends and Patterns of Benzene Concentration and Other Environmental Factors

```{r}
plot_time_series(data_daily, "daily_avg_benzene", "Daily Average Benzene Concentration")
```


# Plot ACF

Plot the ACF of Benzene Concentration to Observe the Autocorrelations

```{r acf}
plot_acf(data_daily, "daily_avg_benzene", "Daily Average Benzene Concentration")
```


# Plot PACF

Plot the PACF of Benzene Concentration to Observe the Partial Autocorrelations

```{r pressure, echo=FALSE}
plot_pacf(data_daily, "daily_avg_benzene", "Daily Average Benzene Concentration")
```


# Hypothesis Testing

Conduct Hypothesis Testing to Check the Stationarity of the Benzene Concentration Time Series

```{r warning=FALSE}
hypothesis_tests <- conduct_hypothesis_testing(data_daily, "daily_avg_benzene")

# Print Detailed Results for Each Test
print(hypothesis_tests$adf_test)
print(hypothesis_tests$kpss_test)
```
