---
title: "Data Pre-Processing"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../src/data_preprocessing.R")
load("../data/processed/data_daily")
```


# Introduction

This notebook outlines the data pre-processing steps for the air quality dataset, focusing on preparing the data for modeling. The steps include checking for stationarity, performing optional feature engineering, and splitting the data into training and testing sets.


# Check Stationarity

Check the Stationarity of the Benzene Concentration Time Series

```{r stationarity}
plot_time_series(data_daily, "daily_avg_benzene", "Daily Average Benzene Concentration")
plot_acf(data_daily, "daily_avg_benzene", "Daily Average Benzene Concentration")
plot_pacf(data_daily, "daily_avg_benzene", "Daily Average Benzene Concentration")
```

```{r}
benzene <- ts(data_daily["daily_avg_benzene"], frequency = 7)
benzene_diff <- diff(benzene, lag = 7)
benzene_diff_diff <- diff(benzene_diff, lag = 1)
tsdisplay(benzene)
tsdisplay(benzene_diff)
tsdisplay(benzene_diff_diff)
```

```{r warning=FALSE}

hypothesis_tests_diff <- conduct_hypothesis_testing(as.data.frame(benzene_diff), "daily_avg_benzene")
hypothesis_tests_diff_diff <- conduct_hypothesis_testing(as.data.frame(benzene_diff_diff), "daily_avg_benzene")

print(hypothesis_tests_diff$adf_test) # Stationary
print(hypothesis_tests_diff$kpss_test) # Stationary

print(hypothesis_tests_diff_diff$adf_test) # Stationary
print(hypothesis_tests_diff_diff$kpss_test) # Stationary
```

Check the Stationarity of the Benzene Concentration Time Series

```{r pressure, echo=FALSE}
hypothesis_tests <- conduct_hypothesis_testing(data_daily, "daily_avg_benzene")

# Print Detailed Results for Each Test
print(hypothesis_tests$adf_test) # Stationary
print(hypothesis_tests$kpss_test) # Almost Non-Stationary
```


# Feature Engineering 

Create Interaction Feature Between Temperature and Humidity

```{r}
#data <- feature_engineering(data)
```


# Split Data into Training and Testing Sets

Split the Data Into Training and Testing Sets Based on a Specified Datetime

```{r}
split_datetime <- "2005-03-10 00:00:00"  # Specify Datetime for the Split
split <- split_data(data_daily, split_datetime)
train_data <- split$train
test_data <- split$test
head(train_data)
head(test_data)
```


# Save Clean Dataset

Save the Clean Dataset to for Modeling

```{r}
ts_data <- ts(data_daily["daily_avg_benzene"], frequency = 7)
ts_train_data <- ts(train_data["daily_avg_benzene"], frequency = 7)
ts_test_data <- ts(test_data["daily_avg_benzene"],start = c(53,3) , frequency = 7)
ts_train_data_s <- diff(diff(ts(train_data["daily_avg_benzene"], frequency = 7), lag = 7), lag = 1)
ts_test_data_s <- diff(diff(ts(test_data["daily_avg_benzene"],start(end(ts_train_data_s)), frequency = 7), lag = 7), lag = 1)
```

```{r}
save(ts_train_data, file = "../data/processed/ts_train_data")
save(ts_test_data, file = "../data/processed/ts_test_data")
```
